\documentclass[sigconf,review]{acmart}

\usepackage{amsmath,amssymb,amsfonts,latexsym}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{epsf,picinpar}
\usepackage{varioref}
\usepackage{colortbl,multirow,hhline}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{colortbl,multirow,hhline}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[normalem]{ulem}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{xcolor,colortbl}
\usepackage{url}
\usepackage{balance}
\usepackage{graphicx, subfigure}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{listings}
\usepackage{framed}
\usepackage{morefloats}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{pdfpages}
\usepackage{fancybox}
\usepackage{amsmath}
\usepackage{flushend}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[acronym]{glossaries}
\usepackage{wrapfig}

% \usepackage[table]{xcolor}


\renewcommand{\ttdefault}{cmr}

%\newcommand{\limit}[1]{\textcolor{red}{\noindent \ding{46}~Page limit:~#1}\\}
\newcommand{\todo}[1]{\textcolor{red}{\ding{46}~#1}} 
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\etal}{\emph{et~al.}\xspace} 

%%% ----- ACRONYMS ----- %%%
\makeglossaries
\newacronym{plt}{PLT}{Page Load Time}
\newacronym{js}{JS}{JavaScript}
\newacronym{pwas}{PWAs}{Progressive Web Applications}
\newacronym{pwa}{PWA}{Progressive Web Application}

\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmcopyright}
\acmConference[Green Lab 2020/2021]{Green Lab 2020/2021 - Vrije Universiteit Amsterdam}{September--October, 2020}{Amsterdam, The Netherlands}
\acmBooktitle{Green Lab 2020/2021 - Vrije Universiteit Amsterdam, September--October, 2020, Amsterdam (The Netherlands)}
    
\begin{document}

\title{
	The Impact of Cluttered JavaScript Code in Mobile Web Apps with respect to Energy Consumption
}


\author{Geoffrey van Driessel}
\affiliation{%
 \institution{2639310 \\ VU Amsterdam}
} \email{g.r.van.driessel@student.vu.nl}

\author{Abijith Radhakrishnan}
\affiliation{%
 \institution{2667575 \\ VU Amsterdam}
} \email{a.radhakrishnan@student.vu.nl}

\author{Sophie Vos}
\affiliation{%
 \institution{2551583 \\ VU Amsterdam}
} \email{s.o.vos@student.vu.nl}

\author{Marc Wiggerman}
\affiliation{%
 \institution{2653796 \\ VU Amsterdam}
} \email{m.g.wiggerman@student.vu.nl}

% \author{Name Surname}
% \affiliation{%
%  \institution{Student Number \\ VU Amsterdam}
% } \email{xyz@student.vu.nl}

\begin{abstract}
\noindent \textit{Context}. 
Mobile phones are a major contributor to global internet traffic. Although, the energy usage of a single smartphone may be considered modest, the overall energy footprint left by mobile devices is far higher. Thiagarajan et al.~\cite{thiagarajan2012battery}, showed that JavaScript (JS) code mainly contributes to the energy consumption relative to other web elements. Chaqfeh et al.\cite{chaqfeh2020jscleaner}~introduced a tool, called \textit{JSCleaner}, that de-clutters mobile web apps by removing non-essential JS code. They showed that this positively influences the Page Load Time. 

\noindent \textit{Goal}. 
Since energy-efficiency contributes to the user experience and the environmental impact of increasingly popular mobile web apps, we aim to contribute by investigating the impact of cluttered JS code on energy consumption. The goal of our study is: ``Analyze cluttered JS code for the purpose of evaluation with respect to the energy consumption from the point of view of software developers in the context of mobile web apps".

\noindent \textit{Method}. 
To accomplish this goal, we conducted an empirical experiment to measure and compare the energy consumption of cluttered and de-cluttered mobile web apps. We randomly selected 27 diverse, currently operational mobile web apps as subjects. Furthermore, we used Android Runner and the Batterystats profiler to measure the energy consumption. 

\noindent \textit{Results}. We tested the energy consumption for small, medium, and large mobile web apps. Our results showed that cluttered mobile web apps do not influence the energy consumption. 

\noindent \textit{Conclusions}. Hence, based on this experiment, we do not recommend developers who aim to reduce the energy consumption of their mobile web app to apply a de-cluttering engine. It should be noted that we tested the difference in energy consumption using a relatively small dataset and using a single de-cluttering engine. Therefore, further research is required to support this claim.
\end{abstract}

\maketitle

\input{intro}
\input{related}
\input{definition}
\input{planning} 
\input{execution} 
\input{results}
\input{discussion}
\input{threats}
\input{conclusion} 

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
